---  
title: "scRNA-seq: Mouse Integration Mini Report"
author: "SysBioLab"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<!-- Sergio Alías, 20231115 -->
<!-- Last modified 20231218 -->

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>

<style>
.dropdown-content {
  display: none;
}

.dropdown:hover .dropdown-content {
  display: block;
}
</style>

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>

# Integration of all samples: WT vs mutant

```{r setup, include = FALSE}
library(Seurat)
library(dplyr)
library(gridExtra)
library(RColorBrewer)
library(ggplot2)
library(scCustomize)
seu <- readRDS(file.path("outs", "seu.mouse.RDS"))
seu.markers <- readRDS(file.path("outs", "seu.markers.mouse.RDS"))
```

### UMAP

```{r c10, echo = FALSE, results = "asis"}
DimPlot(seu, reduction = "umap", label = TRUE, repel = TRUE)
```

```{r c20, echo = FALSE, results = "asis"}
DimPlot(seu, reduction = "umap", split.by = "genotype")
```

```{r c30, echo = FALSE, results = "asis"}
DimPlot(seu, reduction = "umap", group.by = "genotype")
```

### Marker genes

#### Top 10 markers

```{r c40, echo = FALSE, results = "asis"}
grid.table(slice_max(seu.markers, n = 10, order_by = avg_log2FC))
```

#### Canonical markers

```{r ccc0, echo = FALSE, results = "asis"}
can.mark <- c("Abca2",
              "Abcb9")
```

```{r cc40, echo = FALSE, results = "asis"}
grid.table(seu.markers[can.mark,][complete.cases(seu.markers[can.mark,]),])
```

### Markers expression

#### Top 10 markers

```{r c60, echo = FALSE, results = "asis", fig.show="hold", out.width="100%", fig.height = 20}
Stacked_VlnPlot(seu,
        ncol = 1,
        features = slice_max(seu.markers, n = 10, order_by = avg_log2FC)$gene,
        pt.size = 0,
        x_lab_rotate = 45)
```

#### Canonical markers

```{r cc60, echo = FALSE, results = "asis", fig.show="hold", out.width="100%", fig.height = 4}
Stacked_VlnPlot(seu,
        ncol = 1,
        features = seu.markers[can.mark,][complete.cases(seu.markers[can.mark,]),]$gene,
        pt.size = 0,
        x_lab_rotate = 45)
```

### Canonical markers expression pattern

```{r cc70, echo = FALSE, results = "asis", warning = FALSE, fig.show="hold", out.width="100%", message = FALSE}
colGEX <- c("grey85", brewer.pal(7, "Reds"))
plotTheme <- theme_classic(base_size = 18)

for (i in seu.markers[can.mark,][complete.cases(seu.markers[can.mark,]),]$gene){
print(FeaturePlot_scCustom(seu, reduction = "umap", pt.size = 0.1, num_columns = 1, label = TRUE,
                  features = i, order = TRUE, repel = TRUE) &
  scale_color_gradientn(colors = colGEX) & plotTheme & coord_fixed())
}
```

### Dotplot for cell type annotation


```{r ccc1, echo = FALSE, results = "asis"}
can.mark.dp <- c("Nrl",
                 "Arr3",
                 "Rlbp1",
                 "Scgn",
                 "Sebox",
                 "Slc6a9",
                 "Gad1",
                 "Thy1",
                 "Onecut2",
                 "Cx3cr1",
                 "Pecam1",
                 "Acta2",
                 "Hbb-bs")
```

```{r cc80, echo = FALSE, results = "asis", fig.show="hold", out.width="100%", fig.height = 5}
DotPlot_scCustom(seu,
                 features = rev(can.mark.dp),
                 flip_axes = TRUE,
                 colors_use =  colGEX,
                 x_lab_rotate = 45)
```

### DEgenes: volcano plots

```{r vol, echo = FALSE, results = "asis", warning = FALSE, fig.show="hold", out.width="100%", message = FALSE}

DE.markers <- readRDS(file.path("outs", "mouse_markers_logfc01_pval05.RDS"))

for (i in seq_along(DE.markers)){
  if (nrow(DE.markers[[i]] > 0)){
  print(EnhancedVolcano::EnhancedVolcano(DE.markers[[i]],
                                         lab = rownames(DE.markers[[i]]),
                                         x = 'avg_log2FC',
                                         y = 'p_val_adj',
                                         title = names(DE.markers)[[i]],
                                         pCutoff = 0.05,
                                         FCcutoff = 0.1))
  }
}
```